---
title: 'RMarkdown Appreciation'
date: '12-Nov-2019'
author:
- affiliation: Sister Analyst
  name: Tatjana Kecojevic
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    code_download: true
    df_print: kable
params:
  data: "data/exyu_olympic.csv"
---  

This document provides answers for the `rmarkdown` appreciation study as of `r rmarkdown::metadata$date`. It will include both: the rcode and its output.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(here) # for file paths
library(tidyverse) # for all else
theme_set(theme_minimal())
```


```{r include=FALSE}
exyu <- read.csv(here(params$data))
```

Let us have a look at data using `glimpse()` function.
```{r}
glimpse(exyu)
```

## Task 1

**Find the number of medals per each team?** 

```{r}
exyu %>% 
  filter(!is.na(Medal)) %>% 
  group_by(Team, Medal) %>% 
  summarize(cases=n()) %>% 
  DT::datatable()
```

## Task 2

**Find the number of medals per each team for the last Rio games?**

```{r}
exyu %>% 
  filter(!is.na(Medal) & Year == 2016) %>% 
  group_by(Team, Medal) %>% 
  summarize(cases=n()) %>% 
  DT::datatable()
```

## Task 3

**Visualise data about number of female and male athletes from ex YU countries available in the data set:**

1) identify data to be poloted

2) visualise data

### 1: Identify data

```{r}
exyu_mf <- exyu %>% 
  group_by(Team, Sex) %>% 
  summarize(total = n()) #<< 
exyu_mf
```

### 2: How do we plot this? 

We need a bar chart with each team on the x axis and a number of male and female athlethes on the y axis.

```{r}
ggplot(data = exyu_mf, aes(x = Team, y = total, fill = Sex)) +
  geom_bar(stat="identity",  position="dodge", col = "black") +
  # to make it read easier flip x & y coordinates
  coord_flip() +
  # add description for x and y axies and title and subtitle  
  labs(x="ex YU country", y="No of athletes", 
       title = "Comparisons of M and F representatives in exYU Teams",
       subtitle = "for klikR workshop",
       caption = "Data from: kaggle - 120 years of Olympic history") +
  # add the border on the graph  
  theme(panel.border = element_rect(fill = NA, colour = "black", size = 1)) +
  # remove the grid lines
  theme(plot.title = element_text(size = 14, vjust = 2),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_blank())
```