---
title: "RMarkdown Appreciation"
description: |
  Examples for doing RR in R
author: 
  - name: "Tatjana Kecojevic, Ph.D."
    url: https://tanjakec.github.io
    affiliation: Sister Analyst
    affiliation_url: http://sisteranalyst.org/
  - name: "Balsa Delibasic, Ph.D."  
    url: http://www.instifdt.bg.ac.rs/researcher/balsa-delibasic/
    affiliation: Intitute of Philosophy and Social Theory
    affiliation_url: http://www.instifdt.bg.ac.rs/en/
  - name: "Srdjan Prodanovic, Ph.D."  
    url: http://www.instifdt.bg.ac.rs/researcher/srdan-prodanovic/
    affiliation: Intitute of Philosophy and Social Theory
    affiliation_url: http://www.instifdt.bg.ac.rs/en/
creative_commons: CC BY
date: "2019-11-12"
output:   
  distill::distill_article:
    toc: true
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = NA
)
```

```{r}
library(dplyr) 
library(ggplot2)
```

This document provides answers for the `rmarkdown` appreciation study as of `r rmarkdown::metadata$date`. It will include both: the rcode and its output.


```{r}
exyu <- read.csv("data/exyu_olympic.csv")
```

Let us have a look at data using `glimpse()` function.

```{r}
glimpse(exyu)
```

## Task 1

**Find the number of medals per each team?** 

```{r}
exyu %>% 
  filter(!is.na(Medal)) %>% 
  group_by(Team, Medal) %>% 
  summarize(cases=n()) %>% 
  knitr::kable(format = "markdown")
```

## Task 2

**Find the number of medals per each team for the last Rio games?**

```{r}
exyu %>% 
  filter(!is.na(Medal) & Year == 2016) %>% 
  group_by(Team, Medal) %>% 
  summarize(cases=n()) %>% 
  DT::datatable()
```

## Task 3

**Visualise data about number of female and male athletes from ex YU countries available in the data set:**

1) identify data to be poloted

2) visualise data

### 1: Identify data

```{r}
exyu_mf <- exyu %>% 
  group_by(Team, Sex) %>% 
  summarize(total = n()) #<< 
exyu_mf

exyu_mf
```

### 2: How do we plot this? 

We need a bar chart with each team on the x axis and a number of male and female athlethes on the y axis.

```{r}
ggplot(data = exyu_mf, aes(x = Team, y = total, fill = Sex)) +
  geom_bar(stat="identity",  position="dodge", col = "black") +
  # to make it read easier flip x & y coordinates
  coord_flip() +
  # add description for x and y axies and title and subtitle  
  labs(x="ex YU country", y="No of athletes", 
       title = "Comparisons of M and F representatives in exYU Teams",
       subtitle = "for klikR workshop",
       caption = "Data from: kaggle - 120 years of Olympic history") +
  # add the border on the graph  
  theme(panel.border = element_rect(fill = NA, colour = "black", size = 1)) +
  # remove the grid lines
  theme(plot.title = element_text(size = 14, vjust = 2),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_blank())
```

## Acknowledgments {.appendix}

Our thanks to all the research present in the workshop.

## Author Contributions {.appendix}

Tatjana Kecojevic prepared and delivered the workshop material. Balsa Delibasic and Srdjan Prodanovic for organised the event.