---
title: "RMarkdown Appreciation"
author:
 - name: "Tatjana Kecojevic, Ph.D."
   affiliation: "1"
 - name: "Aleksandar Linc Djordjevic, MSc."
   affiliation: "2"
 - name: "Brian Cox, Ph.D."
   affiliation: "3"
address:
 - code: "1"
   address: Sister Analysis, Belgrade, Serbia
 - code: "2"
   address: Data Science Conference Europe, Belgrade, Serbia
 - code: "3"
   address: University of Manchester, School of Physics and Astronomy, Oxford Road, Manchester, M13 9PL UK
#bibliography: sample.bib
params:
  palette: 
    label: "scico palette:"
    value: roma
    input: select
    choices: [berlin, roma, cork, grayC]
output: 
  bookdown::word_document2: default
  bookdown::html_document2: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = here::here("images/")
)
surv_cols <- scico::scico(3, begin = .3, end = 1, palette = params$palette)
```

```{r, include = FALSE}
source(here::here("R/script1.R"))
```

# Title Page

Title:  RMarkdown Appreciation


Authors: Author One1, Author Two2, Author Three3

Affiliations: 1. Sister Analysis
2. West University of Timisoara
3. University of Manchester

Corresponding Author:
Author One,
Sister Analyst
11080, Zemun
Serbia

Tel: 555-555-5555
Fax: 555-555-7890
Email: author_one@sisteranalyst.org

Running Title: Mock Publication
Word Count: 1000

# Abstract

Assessing the accuracy of the given quantile parametric re-
gression function estimate requires valid and reliable procedures for es-
timating the asymptotic variance-covariance matrix of the estimated pa-
rameters. This covariance matrix depends on the reciprocal of the density
function of the error (sparsity function) evaluated at the quantile of in-
terest which, particularly for heteroscedastic non-iid cases, results in a
complex and dificult estimation problem. It is well-known that the con-
struction of confidence intervals based on the quantile regression estimator
can be simplified by using a bootstrap. To construct confidence intervals
in quantile regression we propose an effective and easy to apply bootstrap
method based on the idea of Silverman's kernel smoothing approach. This
proposed bootstrapping method requires the estimation of the conditional
variance function of the fitted quantile. In this paper we will discuss a
variety of approaches to estimate the conditional variance function. These
will include the adaptation of GLMs as well as non-parametric regression
based estimation. These diferent approaches have been assessed under
various data structures simulated in R and compared to several exist-
ing methods computable in the quantreg package contributed by Roger
Koenker. This methodology is also applicable to a wider class of regression
models with heteroscedastic errors where the transformation to normality
is difcult to achieve or maybe undesirable given a need to preserve the
original data scale.

METHODS
Explain the methodology

RESULTS
Describe the results

CONCLUSIONS
Provide a conclusion

# Introduction

Here is the text of your introduction.

# Section 1

Some introduction

## Section 1.1

Some analysis

# Section 2

Some discussion

# Conslucion

What we've learnt

# Citations

Blabla \cite{Lannes} blabla. Blabla \cite{HJ2} blabla. Blabla \cite{BF, Lannes} blabla. Blabla \cite{Benjamin1967, HJ2, HJ3, HP2} blabla.